---
title: "HomeownershipRates"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Homeownership Rates

One measure that assesses the strength of the housing market is homeownership rates, which can be defined as the proportion of all households in the nation that are owner-occupied. 

This plot shows homeownership rates by race since 1994 until 2016.

While homeownership rates have increased steadily until 2004, the began falling prior to the beginning of the Great Recession. In 2016, the trend has begun to increase again.

While this pattern is true for the entire population in the U.S., the breakdown of the data by race shows sever disparities in homeownership. 

## Load and Process the Data

```{r echo = TRUE, eval=TRUE, results="hide", message=FALSE, warning=FALSE}
library(dmm)

home <- read.csv("HomeownershipByRace.csv")
home <- as.data.frame(t(home))
home <- home[-1,]
colnames(home) <- c("U.S. total", "White", "Black", "American Indian or Alaskan Native", "Asian or Native Hawaiian/Pacific Islander","Hispanic or Latino", "Non-Hispanic")
rownames(home) <- seq(1994, 2016)
home$`U.S. total`<- unfactor(home$`U.S. total`)
home$White <- unfactor(home$White)
home$Black <- unfactor(home$Black)
home$`American Indian or Alaskan Native` <- unfactor(home$`American Indian or Alaskan Native`)
home$`Asian or Native Hawaiian/Pacific Islander` <- unfactor(home$`Asian or Native Hawaiian/Pacific Islander`)
home$`Hispanic or Latino` <- unfactor(home$`Hispanic or Latino`)
home$`Non-Hispanic` <- unfactor(home$`Non-Hispanic`)
```

## Show the Plotly Code
```{r echo = TRUE, eval=TRUE, results="hide", message=FALSE, warning=FALSE}
library(plotly)

p <- plot_ly(data=home, x=as.integer(rownames(home))) %>%
  add_trace(y=home$`U.S. total`, name="U.S. Total", type='scatter', mode='lines') %>%
  add_trace(y=home$White, name='White', type='scatter', mode='lines') %>%
  add_trace(y=home$Black, name='Black', type='scatter', mode='lines') %>%
  add_trace(y=home$`American Indian or Alaskan Native`, name='American Indian or Alaskan Native', type='scatter', mode='lines') %>%
  add_trace(y=home$`Asian or Native Hawaiian/Pacific Islander`, name='Asian or Native Hawaiian/Pacific Islander', type='scatter', mode='lines') %>%
  add_trace(y=home$`Hispanic or Latino`, name='Hispanic or Latino', type='scatter', mode='lines') %>%
  add_trace(y=home$`Non-Hispanic`, name='Non-Hispanic', type='scatter', mode='lines') %>%
  layout(title="Homeownership Rates by Race, 1994-2016", xaxis=list(title="Year"), yaxis=list(title="Percentage"))
```

## The Actual Plot
```{r echo = FALSE}
p
```